#Ansm website contains data on FDA Drug shortage. It is an unstructured data, unlike HTML tables, so our task woudl be to scrape 
refine and convert it in a useable format.

#### global options to suppress warnings and messages in final document.
#### They are still visible in the compilation log in R.

#### Each of these options can also be set per-chunk, i.e.,
#### ```{r, fig.width = 5} 
#### ... 
####```
knitr::opts_chunk$set(message = FALSE, ## supress general messages
                      warning = FALSE, ## supress warnings
                      fig.height = 4, fig.width = 4, ## set figure size (inches)
                      cache = TRUE ## cache code so compilation is faster
                                   ## only runs if chunk is modified
                      )

```


`First we load the required libraries`

```{r}
library(rvest)
library(stringr)
```


`We move ahead with grabbing the url and extracting the links, which contains the data that concerns us`

```{r}
an_main <- html("http://www.ansm.sante.fr/S-informer/Informations-de-securite-Ruptures-de-stock-des-medicaments")
an <- an_main%>% html_nodes("div a")%>%html_attr(name="href")
```


##Regular expression to improve the links

```{r}
ang <- grep("^/S-informer/Informations-de-securite-Ruptures-de-stock-des-medicaments.*$", an)
anm <- an[ang]
anm <- str_c("http://www.ansm.sante.fr",anm)
an_sm <- anm[-c(1,2)]
```


###Get the main link with which remaining parts will collaborate.

```{r}
an_m <- html("http://www.ansm.sante.fr/S-informer/Informations-de-securite-Ruptures-de-stock-des-medicaments/ALKONATREM-150-mg-gelule-Chlorhydrate-de-demeclocycline-Rupture-de-stock")%>%
  html_nodes("tr th")%>% html_text()
an_main <-as.data.frame(t(an_m),header=FALSE)
```


####Now we move ahead with sub parts, one by one.

`Indications`

```{r}
Indications <- vector("list", length = (length(an_sm)))
for(i in 1:length(an_sm)){
  print(i)
  # error handling - skips to next URL if it gets an error
  result <- try(
    Indications[i] <- html(an_sm[[i]])%>% html_nodes(".online_editor th+td")%>% html_text()
  ); if(class(result) == "try-error") next;
}
Indications = do.call("rbind", lapply(Indications, "[[", 1))
Indications
```



`Lab operator `

```{r}
Lab_operator <- vector("list", length = (length(an_sm)))
for(i in 1:length(an_sm)){
  print(i)
  # error handling - skips to next URL if it gets an error
  result <- try(
    Lab_operator[i] <- html(an_sm[[i]])%>% html_nodes("tr~ tr+ tr td") %>% html_text()
  ); if(class(result) == "try-error") next;
}
Lab_operator = do.call("rbind", lapply(Lab_operator, "[[", 1))
Lab_operator <- gsub("\n","",Lab_operator)
```

`Reporting origin`

```{r}
Reporting_origin <- vector("list", length = (length(an_sm)))
for(i in 1:length(an_sm)){
  print(i)
  # error handling - skips to next URL if it gets an error
  result <- try(
    Reporting_origin[i] <- html(an_sm[[i]])%>% html_nodes("tr:nth-child(3) td") %>% html_text()
  ); if(class(result) == "try-error") next;
}
Reporting_origin = do.call("rbind", lapply(Reporting_origin, "[[", 1))
Reporting_origin <- gsub("\n","",Reporting_origin)
```


`Date`

```{r}
Date <- vector("list", length = (length(an_sm)))
for(i in 1:length(an_sm)){
  print(i)
  # error handling - skips to next URL if it gets an error
  result <- try(
    Date[i] <- html(an_sm[[i]])%>% html_nodes("tr:nth-child(4) td") %>% html_text()
  ); if(class(result) == "try-error") next;
}
Date = do.call("rbind", lapply(Date, "[[", 1))
Date <- sub("^.+([0-9][0-9]/[0-9][0-9]/[0-9][0-9][0-9][0-9]).+$","\\1",Date)
Date
```

`Specific comments`

```{r}
Specific_comments <- vector("list", length = (length(an_sm)))
for(i in 1:length(an_sm)){
  print(i)
  # error handling - skips to next URL if it gets an error
  result <- try(
    Specific_comments[i] <- html(an_sm[[i]])%>% html_nodes("td div") %>% html_text()
  ); if(class(result) == "try-error") next;
}
Specific_comments = do.call("rbind", lapply(Specific_comments, "[[", 1))
Specific_comments <- gsub("\n","",Specific_comments)
```


#Now combining all the parts together and structuring them in tabular form


```{r}
ansm_full <- cbind(Indications,Lab_operator,Reporting_origin,Date,Specific_comments)
ansm_view <- rbind(an_main,ansm_full)
colnames(ansm_view) <- c("Indication","Lab operator", "Reporting Origin",
                         "Date","Specific Comments")
ansm_view <- ansm_view[-1,]


`Attach links for the references`

ansm_view$links <- an_sm

#To view the data

View(ansm_view)
```

